Starspots on sub sub giants

### 2018-10-16 document/ms.tex

\shorttitle{Spots on Sub-sub-giants}

@@

We do not know what causes some sub-sub giants!

%Fill in more thereoy here
\citet{somers15} emphasized the roll of starspots in inferring stellar ages.

>>>>

\shorttitle{Spots on Sub-subgiants}

@@

We do not know what causes some sub-sub giants!
But now we know a little... more. Hence this paper!

%Fill in more theory here
\citet{somers15} emphasized the roll of starspots in inferring stellar ages.

\begin{itemize}
\item What is a sub-subgiant?
  \begin{itemize}
  \item What causes sub sub giant stars (Leiner et al. 2017)
  \end{itemize}
\item M67 S1063
\begin{itemize}
  \item Prototypical subsub (Geller et al. 2017)
  \item Binary orbit, SB1
\end{itemize}
\item Starspots as confounding factors
\begin{itemize}
  \item Inhibit convective efficiency (redder and bigger)
  \item Also confound observations: assign incorrect Teff
  \item This paper aims to measure the starspot coverage and temp
\end{itemize}
\item Layout of this paper
\end{itemize}

\section{Observation and data reduction}
\begin{itemize}
\item IGRINS observations
\item Ground-based photometric monitoring- ASASSN, AAVSO, ASAS
\item K2 data (Campaign 5), *stretch goal* C16
\item *stretch goal* APOGEE?
\item Gaia data (membership confirmed)
\end{itemize}

\section{Analysis}
\begin{itemize}
\item Summary and assumptions of our methods
\item K2 Superstamp(s)
\begin{itemize}
  \item K2 detrending
  \item Interpreting lightcurves
  \item Period and amplitude of lightcurve, with multi-term Lomb-Scargle + Fourier reconstruction
\end{itemize}
\item Phase folded archival V-band photometry (ASASSN+)
\item IGRINS two-temperature spectral inference w/ Starfish
\begin{itemize}
  \item MCMC convergence and posterior predictive checks
  \item FIGURE: IGRINS Spectra
  \item Internal consistency of vsini, $v_z$
  \item FIGURE: Violin plot
\end{itemize}
\item Analysis of near-IR flux contribution from binary companion
\begin{itemize}
  \item Limits on companion types
\end{itemize}
\end{itemize}

\section{Results}
\begin{itemize}
\item We detect spots in spectra
\begin{itemize}
  \item S1063 has ~X\% coverage fraction of spots with Tspot ~ Y based on IGRINS + Starfish
  \item *bonus* Revised effective temperature using both temperature components $[f_{\textrm{spot}} * T_{\textrm{spot}}^4 + (1 -f_{\textrm{spot}}) * T_{\textrm{ambient}}^4] = T_{\textrm{eff}}^4$
  \item *bonus* Rsini
\end{itemize}
\item IGRINS observations occurred at maximum of lightcurve, so total spot coverage is even greater
\item FIGURE: $T_{spot}$ versus $f_{spot}$ plot
\item What coverage fraction would we have measured across the rotational phase?
\end{itemize}

\section{Discussion}
\begin{itemize}
\item Spot coverage is consistent with formation theories
\item Conceivable geometries with circumpolar active longitudes, or migrating active latitudes
\item Biases introduced if we assume a spot-free model
\begin{itemize}
  \item Where does subsub sit in a new HR diagram? (new Somers models)
  \item *bonus* FIGURE: PMS HR diagram with new Somers tracks
  \item Spot impact on SED fits
\end{itemize}
\end{itemize}
